Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
add igv screenshot meth

>>>>

Location of methylation across the genome varies across taxa. Here is what you might expect to see in a marine invertebrate.

```{r meth-igv, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/igv.png")
```
*Screenshot from IGV. Bedgraph files are displayed. See below for code to create these file (File Conversion)*
